\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[left=0.7in,right=0.7in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black,
    pdftitle={Anand Pattar Resume},
    pdfauthor={Anand Pattar},
    pdfsubject={Full Stack Developer Resume},
    pdfkeywords={MERN, React, Node.js, Express, MongoDB, Full Stack}
}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\itemsep}{0pt}
\setlength{\topsep}{0pt}
\setlist{nosep}

\titleformat{\section}{\normalfont\Large\bfseries\raggedright}{}{0em}{}[\vspace{-0.2em}\hrule\vspace{-0.2em}]
\titlespacing*{\section}{0pt}{0.5em}{0.2em}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\Huge \bfseries Anand Pattar} \\
    \vspace{0.1em}
    \href{mailto:anandpattar7353@gmail.com}{anandpattar7353@gmail.com} \hspace{0.5em}|\hspace{0.5em}
    \href{https://www.linkedin.com/in/anand-pattar-9532a1330}{LinkedIn}
\end{center}

\section*{Summary}
\begin{itemize}
    \item Aspiring Full Stack Developer specializing in MERN stack, focused on building scalable, secure, and user-friendly web applications.
    \item Proficient in React, Node.js, Express.js, and MongoDB, actively exploring authentication, role-based access, and cloud deployment.
    \item Passionate about solving real-world problems through code and continuously enhancing skills to contribute to impactful projects.
\end{itemize}

\section*{Skills}
\begin{minipage}[t]{0.49\textwidth}
    \begin{itemize}[label={}]
        \item \textbf{Programming Languages:} JavaScript
        \item \textbf{Frameworks \& Libraries:} React, Node.js, Express.js, MongoDB
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}
    \begin{itemize}[label={}]
        \item \textbf{Tools \& Technologies:} Git, GitHub, JWT, Netlify, Render
        \item \textbf{Concepts:} Full Stack Development, RESTful APIs, UI/UX
    \end{itemize}
\end{minipage}
\vspace{-0.5em}

\section*{Experience}
\textbf{Full Stack Developer (Learner / Project-Focused)} \hfill \textbf{July 2025 - Present} \\
Self-Learning Projects \hfill Bengaluru, Karnataka, India
\begin{itemize}
    \item Developed full stack web applications using MERN stack (MongoDB, Express.js, React, Node.js) for practical experience.
    \item Applied frontend, backend, and database integration best practices, focusing on modular and maintainable codebases.
    \item Explored and implemented deployment strategies, cloud hosting, and authentication mechanisms for production-ready applications.
\end{itemize}

\section*{Projects}
\textbf{E-commerce Application}
\begin{itemize}
    \item Designed and implemented a full-stack e-commerce platform using MERN stack, integrating user authentication and product management.
    \item Developed RESTful APIs with Node.js and Express.js for product catalog, shopping cart, and order processing functionalities.
    \item Utilized MongoDB for efficient data storage and React for a dynamic, responsive user interface.
\end{itemize}

\textbf{Blog Platform}
\begin{itemize}
    \item Built a dynamic blog platform with MERN stack, enabling users to create, read, update, and delete posts.
    \item Implemented JWT authentication for secure user access and role-based authorization for content management.
    \item Deployed the application using Netlify/Render, ensuring continuous integration and accessibility.
\end{itemize}

\textbf{Real-Time Chat Application}
\begin{itemize}
    \item Developed a real-time chat application leveraging MERN stack, demonstrating proficiency in WebSocket integration for instant messaging.
    \item Managed user sessions and message persistence using MongoDB, ensuring a seamless communication experience.
    \item Focused on responsive design and efficient data handling to support concurrent users.
\end{itemize}

\textbf{To-Do Application}
\begin{itemize}
    \item Created a comprehensive To-Do application using MERN stack, featuring task creation, editing, deletion, and status updates.
    \item Implemented robust backend APIs with Node.js/Express.js and a responsive frontend with React.
    \item Ensured data persistence and user-specific task management through MongoDB integration.
\end{itemize}

\section*{Education}
\textbf{Rani Channamma University, Belagavi} \hfill \textbf{2023 - 2026}

\section*{Certifications}
\begin{minipage}[t]{0.49\textwidth}
    \begin{itemize}
        \item Certificate of Participation -- Masterclass on Roadmap to Becoming a Full Stack Developer
        \item Vibe Coding 101 with Replit
        \item Deloitte Australia - Technology Job Simulation
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}
    \begin{itemize}
        \item From Idea to Interface: A UI/UX Guide to Lovable AI Tools -- Masterclass (PW Skills)
        \item Web Designing Basics
    \end{itemize}
\end{minipage}
\vspace{-0.5em}

\end{document}